Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-20 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny reviewer1 reviewer2

\noindent
\item\comment{My third concern is the use of L-J potential. In practice, the
vesicle surface would be coated with some adhesive molecules (e.g.
receptor/ligand). Is the L-J type adhesive field appropriate for such
interactions? ALso, in reality, these bonds are stochastic in nature.}
\begin{itemize}
  \item We thank the referee for this point. We follow the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
  In both papers the L-J potential is used to model the interaction between RBCs. The focus of this work is to show the hydrodynamic implication of such interaction between two vesicles without any coating of adhesive protein macromolecules. Results from these modeling works using L-J potential are found to be in good agreement with experiments and previous modeling results using different adhesion potential (Ziherl and Svetina, PNAS (2007)).

>>>>

\noindent
\item\comment{My third concern is the use of L-J potential. In practice, the
vesicle surface would be coated with some adhesive molecules (e.g.
receptor/ligand). Is the L-J type adhesive field appropriate for such
interactions? ALso, in reality, these bonds are stochastic in nature.}
\begin{itemize}
  \item We thank the referee for this point. 
   In this work we focus on the adhesion effects on the hydrodynamics 
   of two vesicles drawn together by an external flow.
   Thus the L.-J. type potential is to keep the equilibrium distance, 
   following the modeling works on red blood cells (RBCs) by Flormann {\it et al.}, Sci. Rep. (2017) and Hoore {\it et al.} Soft Matt. (2018).
  In both papers the L-J potential is used to model the interaction between RBCs. The focus of this work is to show the hydrodynamic implication of such interaction between two vesicles without any coating of adhesive protein macromolecules. Results from these modeling works using L-J potential are found to be in good agreement with experiments and previous modeling results using different adhesion potential (Ziherl and Svetina, PNAS (2007)).
